---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r echo=TRUE}
act <- read.csv("activity.csv")
library(ggplot2)
library(lattice)
```

## What is mean total number of steps taken per day?
```{r echo=TRUE}
stepsperday <- tapply(act$steps,act$date,sum,na.rm=TRUE)
qplot(stepsperday,binwidth=21194/11)
Mean <- tapply(act$steps,act$date,mean,na.rm=TRUE)  
Median <- tapply(act$steps,act$date,median,na.rm=TRUE)
```
The Mean of Steps per day is`r Mean` and Median is `r Median`.  

## What is the average daily activity pattern?
```{r echo=TRUE}
b <- tapply(act$steps,act$interval,mean,na.rm=TRUE)
x <- unique(act$interval)
plot(as.factor(x),b,type="l",xlab="Interval",ylab="Average Steps",
     col="red")
Max <- b[b==max(b)]
```
Max is the 5 min interval that contains max no. of steps.  

## Imputing missing values
```{r echo=TRUE}
STEPS <- act$steps
STEPS[is.na(STEPS)] <- b
act2 <- data.frame(STEPS,DATE=act$date,INTERVAL=act$interval)
qplot(tapply(act2$STEPS,act2$DATE,sum),binwidth=21153/11)
Mean2 <- tapply(act2$STEPS,act2$DATE,mean)
Median2 <- tapply(act2$STEPS,act2$DATE,median)
```
The Mean of Steps per day is`r Mean2` and Median is `r Median2`.  

## Are there differences in activity patterns between weekdays and weekends?
```{r echo=TRUE}
type <- vector()
v <- weekdays(as.Date(act$date))=="Sunday"
type[v] <- "weekend"
type[!v] <- "weekday"
library("dplyr")
act <- mutate(act,type)
actweek <- filter(act,type=="weekday")
actweend <- filter(act,type=="weekend")
p <- tapply(actweek$steps,actweek$interval,mean,na.rm=TRUE)
p1 <- tapply(actweend$steps,actweend$interval,mean,na.rm=TRUE)
y <- as.data.frame(p)
y1 <- as.data.frame(p1)
colnames(y) <- c("meen")
colnames(y1) <- c("meen")
y <- mutate(y,INTERVAL=x,type="weekdays")
y1 <- mutate(y1,INTERVAL=x,type="weekend")
y2 <- rbind(y,y1)
xyplot(meen~INTERVAL|type,data=y2,layout=c(1,2),type="l",xlab="Mean")
```
